Theoretical evaluation of the potential advantages of cloud IDEs for research and didactics

### 2019-06-21 che.tex
Manual changes, removed 2 weaker sources

As cloud-technology such technologies are referred which achieve five attributes: 
On-demand self-service, broad network-access, resource pooling, rapid elasticity and measured service \cite{ME11}. 
Cloud technology usually splits into two components:  infrastructure  and  services,  where  Docker and Kubernetes are considered infrastructure and provide a  platform  to  host  services.  
Most  of  the  attributes  are (pseudo-) achievable by the infrastructure alone – such as restarting containers. 
Software running as a service can be put into two categories: 
\textit{Cloud ready} – meaning that it can be run in common cloud environments, such as Kubernetes. 
The term cloud ready  does  usually  not  include  live-scalability. Cloud-readiness is mostly achieved by removing dependencies and either running on bare-linux or being ported into a docker-container. 
Lately the term \textit{Cloud native} came up \cite{BI17}, referring to software which is built from the very first steps to run inside the cloud. This kind of software is usually running inside a docker-container and both resilient and elastic by design \cite{TO17}.  
Resilience refers to the ability of handling failure, both from external sources and restarting/configuring themselves.  
Elasticity is the ability to request more resources on demand, performing more computations when required, but also to free the resources if not needed. 
Cloud-ready software usually achieves only a certain degree of resilience.   
Cloud-Native applications are aware of their context and collect meaningful metrics for the platform that they cannot reach other services or need more capacities \cite{MIN18}. 
The applications must also be able to use the gained resources in a productive and healthy way.  
Modern  cloud-platforms  can  perform  pseudo-scalability for cloud ready-services by starting multiple instances of the same service. 
The cloud-platform performs load-balancing between these instances. 
This naive approach can work out fine, but for example starting two services working on the same database will not yield any real scalability. 
Another common problem arises when two services are started on the same machine and need the same port, just to name two problems with cloud ready  software in a cloud environment.

@@

With Che, this kind of Big-Bang-Migration is not possible, as from the very first step it is working inside of a docker-container.
The properties above can be hold with every change to the image and checked in a normal review-process. 
Problems will arise one at a time and be solved one at a time, whether they are about code or operations. 
Che therefore embraces the core-ideas of DevOps \cite{HUE12}\cite{JA16} and agile software development \cite{EBE16}.
That being said, of course it's possible to big-bang-migrate into Che, causing the normal problem mentioned above. 
However, once the errors are resolved, every further development will work more agile by design.

The artifacts (whether containers or pods) produced with Che are self-contained and immutable, therefore every result is reproducible. 
Any further development is incremental on the existing images and keeps old artifacts stable. 
As the code is fully build inside containers and are already run remotely, the famous “It works on my Machine!” is eliminated. 
This does not only enhance deployments, but also has a big impact on quality assurance and the motivation of developers. 
You can keep multiple projects in a single workspace and launch multiple pods at once, running the full environment. 
The behavior of this multi-pod is unified and testable, making a stable release of full environments possible. 
This is one of the primary goals of the DevOps approach \cite{JA16}. 
\subsection{Sharing Results}
The topic \textit{docker for reproducible research} has already been promoted \cite{BO15} and successfully applied to complex topics \cite{ST16} such as machine learning. 
As Clark et al. \cite{CL14} have used code of several repositories provided from their university, most of the projects can be expected scientific or experimental, therefore 50\% of the research results were not reproducible.

@@

Simply providing a technical correct solution (like laboratories) is not enough to provide a good environment.
One student with a better socio-economic background who can afford a 300\$ GPU will have a better baseline for their education. 
This is simply put unfair.
With Che, universities can provide a free, good and accessible development environment for every student.
\section{Conclusion}
\label{sec:Conclusion}
Cloud technology will be dominant in the foreseeable future. 
Not \textit{everything} will be best fit for cloud, but most of the everyday software benefits from the concepts. 
With more and more tools making it easier, it's just a matter of time until cloud-tec becomes standard instead of bonus.

>>>>

As cloud-technology such technologies are referred which achieve five attributes: 
On-demand self-service, broad network-access, resource pooling, rapid elasticity and measured service \cite{ME11}. 
Cloud technology usually splits into two components:  infrastructure  and  services,  where  Docker and Kubernetes are considered infrastructure and provide a  platform  to  host  services.  
Most  of  the  attributes  are (pseudo-) achievable by the infrastructure alone – such as restarting containers. 
Software running as a service can be put into two categories: 
\textit{Cloud ready} – meaning that it can be run in common cloud environments, such as Kubernetes. 
The term cloud ready  does  usually  not  include  live-scalability. Cloud-readiness is mostly achieved by removing dependencies and either running on bare-linux or being ported into a docker-container. 
Lately the term \textit{Cloud native} came up \cite{BI17}, referring to software which is built from the very first steps to run inside the cloud. This kind of software is usually running inside a docker-container and both resilient and elastic by design \cite{TO17}.  
Resilience refers to the ability of handling failure, both from external sources and restarting/configuring themselves.  
Elasticity is the ability to request more resources on demand, performing more computations when required, but also to free the resources if not needed. 
Cloud-ready software usually achieves only a certain degree of resilience.   
Cloud-Native applications are aware of their context and collect meaningful metrics for the platform that they cannot reach other services or need more capacities. 
The applications must also be able to use the gained resources in a productive and healthy way.  
Modern  cloud-platforms  can  perform  pseudo-scalability for cloud ready-services by starting multiple instances of the same service. 
The cloud-platform performs load-balancing between these instances. 
This naive approach can work out fine, but for example starting two services working on the same database will not yield any real scalability. 
Another common problem arises when two services are started on the same machine and need the same port, just to name two problems with cloud ready  software in a cloud environment.

@@

With Che, this kind of Big-Bang-Migration is not possible, as from the very first step it is working inside of a docker-container.
The properties above can be hold with every change to the image and checked in a normal review-process. 
Problems will arise one at a time and be solved one at a time, whether they are about code or operations. 
Che therefore embraces the core-ideas of DevOps \cite{JA16} and agile software development \cite{EBE16}.
That being said, of course it's possible to big-bang-migrate into Che, causing the normal problem mentioned above. 
However, once the errors are resolved, every further development will work more agile by design.

The artifacts (whether containers or pods) produced with Che are self-contained and immutable, therefore every result is reproducible. 
Any further development is incremental on the existing images and keeps old artifacts stable. 
As the code is fully build inside containers and are already run remotely, the famous “It works on my Machine!” is eliminated. 
This does not only enhance deployments, but also has a big impact on quality assurance and the motivation of developers. 
You can keep multiple projects in a single workspace and launch multiple pods at once, running the full environment. 
The behavior of this multi-pod is unified and testable, making a stable release of full environments possible. 
This is one of the primary goals of the DevOps approach \cite{JA16}. 
\newpage
\subsection{Sharing Results}
The topic \textit{docker for reproducible research} has already been promoted \cite{BO15} and successfully applied to complex topics \cite{ST16} such as machine learning. 
As Clark et al. \cite{CL14} have used code of several repositories provided from their university, most of the projects can be expected scientific or experimental, therefore 50\% of the research results were not reproducible.

@@

Simply providing a technical correct solution (like laboratories) is not enough to provide a good environment.
One student with a better socio-economic background who can afford a 300\$ GPU will have a better baseline for their education. 
This is simply put unfair.
With Che, universities can provide a free, good and accessible development environment for every student.
\newpage
\section{Conclusion}
\label{sec:Conclusion}
Cloud technology will be dominant in the foreseeable future. 
Not \textit{everything} will be best fit for cloud, but most of the everyday software benefits from the concepts. 
With more and more tools making it easier, it's just a matter of time until cloud-tec becomes standard instead of bonus.
